---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# redditor

  [![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
   [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
   [![license](https://img.shields.io/badge/license-GPL3-9cf.svg)](https://www.gnu.org/licenses/gpl.html)

Collection and Analysis of Reddit Data in R

## Overview

The goal of {redditor} is to retrieve recent subreddit data for analysis in R.

## Installation

Soon, you will be able to install the released version of {redditor} from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
#install.packages("redditor")
```

You can also install the development version of {redditor} from GitHub with:

```{r gh-installation, eval=FALSE}
install.packages("devtools")
devtools::install_github("bretsw/redditor")
```

## Authentication

The Reddit API requires OAuth2 authentication; [read more here](https://github.com/reddit-archive/reddit/wiki/API). Get started by  create your own appication key at https://www.reddit.com/prefs/apps. Read more about the Reddit API on the [documentation webpage](https://www.reddit.com/dev/api).

Then save your Reddit API token in the `.Renviron` file as **reddit_token**. You can quickly access this file using the R code `usethis::edit_r_environ(scope='user')`. Add a line to this file that reads: `reddit_token="PasteYourGoogleKeyInsideTheseQuotes"`. To read your key into R, use the code `Sys.getenv('reddit_token')`. Note that {redditor} retrieves your saved API key automatically and securely. Once you've saved the `.Renviron` file, quit your R session and restart. {redditor} functions will work for you from now on.

If you need to revisit or edit your Reddit application key, simply visit https://www.reddit.com/prefs/apps in a Web browser.

```{r, eval=FALSE}
usethis::edit_r_environ(scope='user')
```

```{r}
authentication <- 
  httr::POST(
    url = "https://www.reddit.com/api/v1/access_token", 
    httr::add_headers("User-Agent" = Sys.getenv('reddit_user_agent')),
    httr::authenticate(Sys.getenv('reddit_client_id'), 
                       Sys.getenv('reddit_client_token')
    )
  )

httr::stop_for_status(authentication, "authenticate with Reddit")
```

## Usage

The Reddit API rate limit is 60 requests per minute. Each item returned (e.g., a post) is considered a request. So, using the `get_posts()` default to retrieve 100 would be considered 100 requests by the API and requires a pause before running again.

### get_posts()

```{r}
get_posts <-
  function(subreddit, starting_data = NULL, max_posts = 100, starting_point = "") {
    if (max_posts > 1000) {max_posts <- 1000}
    
    authentication <- 
      httr::POST(
        url = "https://www.reddit.com/api/v1/access_token", 
        httr::add_headers("User-Agent" = Sys.getenv('reddit_user_agent')),
        httr::authenticate(Sys.getenv('reddit_client_id'), 
                           Sys.getenv('reddit_client_token')
        )
      )
    
    httr::stop_for_status(authentication, "authenticate with Reddit")
    
    subreddit_response <- 
      httr::GET(
        url = paste0("https://www.reddit.com/r/", subreddit, 
                     "/new.json?limit=100&after=",
                     starting_point),
        httr::add_headers("User-Agent" = Sys.getenv('reddit_user_agent')),
        httr::authenticate(Sys.getenv('reddit_client_id'), 
                           Sys.getenv('reddit_client_token')
        )
      )
    
    subreddit_page <- jsonlite::fromJSON(httr::content(subreddit_response, as = "text"))

    #subreddit_page <- jsonlite::fromJSON(url)

    subreddit_data <- starting_data
    
    if (!exists("subreddit_data")) {
      subreddit_data <- tibble::as_tibble(subreddit_page$data$children$data)
    } else {
      subreddit_data <- 
        dplyr::bind_rows(subreddit_data,
                         tibble::as_tibble(subreddit_page$data$children$data)
        )
    }

    message(paste(nrow(subreddit_data), "posts found so far..."))
    
    if (nrow(subreddit_data) >= max_posts) {
      
      message(paste("Done retrieving. Returned", nrow(subreddit_data), "posts in total."))
      return(subreddit_data)
      
    } else {
      
      message("Going to sleep...")
      Sys.sleep(60)  # Wait 60 seconds before running again to keep below API rate limit 
      message("Waking up...")
      
      get_posts(subreddit = subreddit_data$subreddit[1], 
                starting_data = subreddit_data,
                starting_point = paste0("t3_", tail(subreddit_data$id, 1))
      )
    }
    
  }
```


```{r}
example_subreddit <- get_posts("instructionaldesign")
```

### clean_posts()

```{r}
clean_posts <- function(x) {
  x <- dplyr::rename(x, post_date_time = created_utc)
  
  x <- 
    dplyr::mutate(
      x,
      post_date_time = anytime::anytime(post_date_time, asUTC=TRUE),
      post_date_time = lubridate::ymd_hms(lubridate::as_datetime(post_date_time)),
      post_date_time = lubridate::with_tz(post_date_time, tzone='US/Eastern')
      )
}
```

```{r}
example_subreddit <- clean_posts(example_subreddit)
#table(example_subreddit$id)
#min(example_subreddit$post_date_time)
```

We now have subreddit posts dating back to **`r min(example_subreddit$post_date_time)`**.

## Learning more about {redditor}

For a walkthrough of numerous additional {redditor} functions, visit the [Using {redditor} with a teaching-related subreddit]() vignette webpage.

## Getting help

{redditor} is still a work in progress, so I fully expect that there are still some bugs to work out and functions to document better. If you find an issue, have a question, or think of something that you really wish {redditor} would do for you, don't hesitate to [email Bret](mailto:bret@bretsw.com) or reach out on Twitter: [\@bretsw](https://twitter.com/bretsw).

You can also [file an issue on Github](https://github.com/bretsw/redditor).

## Future collaborations

This is package is still in development, and I welcome new contributors. Just reach out through the same channels as "Getting help."

## License

The {redditor} package is licensed under a *GNU General Public License v3.0*, or [GPL-3](https://choosealicense.com/licenses/lgpl-3.0/). For background on why I chose this license, read Hadley Wickham's take on [R package licensing](http://r-pkgs.had.co.nz/description.html#license).
